
---
pagetitle: palasso
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- Modify xxx.Rmd, not xxx.md! -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/rauschenberger/palasso.svg)](https://travis-ci.org/rauschenberger/palasso)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/rauschenberger/palasso?svg=true)](https://ci.appveyor.com/project/rauschenberger/palasso)
[![Coverage Status](https://codecov.io/github/rauschenberger/palasso/coverage.svg?branch=master)](https://codecov.io/github/rauschenberger/palasso)

## Scope

Sparse regression with paired covariates (extending [glmnet](https://CRAN.R-project.org/package=glmnet)).

## Installation

Install the current release from [CRAN](https://CRAN.R-project.org/package=palasso),
or the latest development version from [GitHub](https://github.com/rauschenberger/palasso):

```{r,eval=FALSE}
install.packages("palasso")
```

```{r,eval=FALSE}
#install.packages("devtools")
devtools::install_github("rauschenberger/palasso")
```

Optionally, install [ashr](https://github.com/stephens999/ashr) and [CorShrink](https://github.com/kkdey/CorShrink) for the correlation shrinkage:

```{r,eval=FALSE}
devtools::install_github("stephens999/ashr")
devtools::install_github("kkdey/CorShrink")
```

## Reference

A Rauschenberger, I Ciocanea-Teodorescu, RX Menezes, MA Jonker, and MA van de Wiel (2019). "Sparse regression with paired covariates". Manuscript in preparation.

[![CRAN version](https://www.r-pkg.org/badges/version/palasso)](https://CRAN.R-project.org/package=palasso)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/palasso)](https://CRAN.R-project.org/package=palasso)
[![Total CRAN downloads](https://cranlogs.r-pkg.org/badges/grand-total/palasso)](https://CRAN.R-project.org/package=palasso)

<!--
(www.r-pkg.org/pkg/palasso)
-->

